Online Verification of Commutativity

### 2020-08-10 acmPaper/paper.tex
typo

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \begin{verbatim}
            var a : meters = 1;
            var b : miles = (miles) a;
            var c : feet = (feet) a;
            define wugs:
                1 miles = 10 wugs;
                1 foot = 10000 wugs;
            var d : wugs = (wugs) a;
        \end{verbatim}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}

>>>>

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \begin{verbatim}
            var a : meters = 1;
            var b : miles = (miles) a;
            var c : feet = (feet) a;
            define wugs:
                1 miles = 10000 wugs;
                1 foot = 10 wugs;
            var d : wugs = (wugs) a;
        \end{verbatim}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}
